---
title: "Hello R"
author: "Prajwal Parajuli"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 10
    fig_height: 10
    highlight: monochrome
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Based on the help file:

- 1846 rows
- 13 columns
- 3 variables 
  - dataset: indicated which dataset the data are from
  - x: x-values
  - y: y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the data in the star dataset.

```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


Comparing the r value between the dino and star dataset indicate that both have very weak linear relationship between the variables.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

### Exercise 4

Plotting the circle dataset.

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Comparing the r value of circle dataset to the dino dataset also indicate very weak negative linear relationship between the variabes and both the r values are very close to each other. 

```{r}
circle_data %>%
  summarize(r = cor(x,y))

```

### Exercise 5

Plotting all the datasets at once. 

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+ 
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")

```

And calculating their summary correlation coefficients.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```